Spring haul-out behavior of seals in the Bering and Chukchi seas

### 2023-09-16 analysis/paper/London_HauloutBeahvior.Rmd
updates to plot titles/subtitles
haul-out heatmap figures updated to address #50

```{r beardedHOCal, include=TRUE, fig.cap="Predicted hourly haul-out probability of bearded seals (all ages and sex classes) from 1 March to 15 July for all and sex classes. Hour of the day was fixed at local solar noon."}

@@

p <- ggplot(plot_df,aes(day,solar_hour,fill = ho_prob))+
  geom_tile(color= "white",size = 0) +
  scale_fill_gradientn(colors = rev(met.brewer("Hiroshige")),
                       name = "haul-out probability", aesthetics = "fill",
                       limits = c(0,1), breaks = c(0.25, 0.50, 0.75),
                       guide = guide_colorbar(title.position = "bottom", barwidth = 15,
                                              barheight = 0.5, title.hjust = 0.5)
  # scale_fill_viridis_c(name = "haul-out probability", aesthetics = "fill",
  #                      guide = guide_colorbar(title.position = "bottom", barwidth = 15,
  #                                             barheight = 0.5, title.hjust = 0.5)
  )
p <- p + facet_grid(age_sex~month)
p <- p + scale_x_continuous(breaks = c(1,10,20,30)) +
  scale_y_continuous(breaks = c(4,12,20))
p <- p + theme(legend.position = "bottom") +
  theme(strip.background = element_rect(colour="white")) +
  theme(axis.ticks=element_blank()) +
  xlab("day of month") + ylab("local solar hour") +
  ggtitle("Bearded seals rest on sea ice around solar noon and solar midnight")
p
```

@@

p <- ggplot(plot_df, aes(day,solar_hour,fill = ho_prob)) +
  geom_tile(color = "white",size = 0) +
  scale_fill_gradientn(colors = rev(met.brewer("Hiroshige")),
                       name = "haul-out probability", aesthetics = "fill",
                       limits = c(0,1), breaks = c(0.25, 0.50, 0.75),
                       guide = guide_colorbar(title.position = "bottom", barwidth = 15,
                                              barheight = 0.5, title.hjust = 0.5)
  # scale_fill_viridis_c(name = "haul-out probability", aesthetics = "fill",
  #                      guide = guide_colorbar(title.position = "bottom", barwidth = 15,
  #                                             barheight = 0.5, title.hjust = 0.5)
  )
p <- p + facet_grid(age_sex~month)
p <- p + scale_x_continuous(breaks = c(1,10,20,30)) +
  scale_y_continuous(breaks = c(4,12,20))
p <- p + theme(legend.position = "bottom") +
  theme(strip.background = element_rect(colour = "white")) +
  theme(axis.ticks = element_blank()) +
  xlab("day of month") + ylab("local solar hour") +
  ggtitle("Ribbon seals rest on sea ice in late spring and around solar noon.")
p
```

@@

p <- ggplot(plot_df,aes(day,solar_hour,fill=ho_prob))+
  geom_tile(color= "white",size = 0) +
  scale_fill_gradientn(colors = rev(met.brewer("Hiroshige")),
                       name = "haul-out probability", aesthetics = "fill",
                       limits = c(0,1), breaks = c(0.25, 0.50, 0.75),
                       guide = guide_colorbar(title.position = "bottom", barwidth = 15,
                                              barheight = 0.5, title.hjust = 0.5)
  # scale_fill_viridis_c(name = "haul-out probability", aesthetics = "fill",
  #                      guide = guide_colorbar(title.position = "bottom", barwidth = 15,
  #                                             barheight = 0.5, title.hjust = 0.5)
  )
p <- p + facet_grid(age_sex~month)
p <- p + scale_x_continuous(breaks = c(1,10,20,30)) +
  scale_y_continuous(breaks = c(4,12,20))
p <- p + theme(legend.position = "bottom") +
  theme(strip.background = element_rect(colour="white")) +
  theme(axis.ticks=element_blank()) +
  xlab("day of month") + ylab("local solar hour") +
  ggtitle("Spotted seals rest on sea ice in late spring and around solar noon.")
p
```

>>>>

```{r beardedHOCal, include=TRUE, fig.cap="Predicted hourly haul-out probability of bearded seals (all ages and sex classes) from 1 March to 15 July for all and sex classes."}

@@

p <- ggplot(plot_df,aes(day,solar_hour,fill = ho_prob))+
  geom_tile(color= "white",size = 0) +
  scale_fill_gradientn(colors = rev(met.brewer("Hiroshige")),
                       name = "haul-out probability", aesthetics = "fill",
                       limits = c(0,1), breaks = c(0.25, 0.50, 0.75),
                       guide = guide_colorbar(title.position = "bottom", barwidth = 15,
                                              barheight = 0.5, title.hjust = 0.5)
  # scale_fill_viridis_c(name = "haul-out probability", aesthetics = "fill",
  #                      guide = guide_colorbar(title.position = "bottom", barwidth = 15,
  #                                             barheight = 0.5, title.hjust = 0.5)
  )
p <- p + facet_grid(age_sex~month)
p <- p + scale_x_continuous(breaks = c(1,10,20,30)) +
  scale_y_continuous(breaks = c(4,12,20))
p <- p + theme(legend.position = "bottom") +
  theme(strip.background = element_rect(colour="white")) +
  theme(axis.ticks=element_blank()) +
  xlab("day of month") + ylab("local solar hour") +
  ggtitle("Bearded seal predicted haul-out probability",
          subtitle = str_wrap("Periods of highest haul-out probability for bearded seals appear to be centered around solar noon and midnight"))
p
```

@@

p <- ggplot(plot_df, aes(day,solar_hour,fill = ho_prob)) +
  geom_tile(color = "white",size = 0) +
  scale_fill_gradientn(colors = rev(met.brewer("Hiroshige")),
                       name = "haul-out probability", aesthetics = "fill",
                       limits = c(0,1), breaks = c(0.25, 0.50, 0.75),
                       guide = guide_colorbar(title.position = "bottom", barwidth = 15,
                                              barheight = 0.5, title.hjust = 0.5)
  # scale_fill_viridis_c(name = "haul-out probability", aesthetics = "fill",
  #                      guide = guide_colorbar(title.position = "bottom", barwidth = 15,
  #                                             barheight = 0.5, title.hjust = 0.5)
  )
p <- p + facet_grid(age_sex~month)
p <- p + scale_x_continuous(breaks = c(1,10,20,30)) +
  scale_y_continuous(breaks = c(4,12,20))
p <- p + theme(legend.position = "bottom") +
  theme(strip.background = element_rect(colour = "white")) +
  theme(axis.ticks = element_blank()) +
  xlab("day of month") + ylab("local solar hour") +
  ggtitle("Ribbon seal predicted haul-out probability.",
          subtitle = str_wrap("Periods of highest haul-out probability for ribbon seals appear centered around solar noon and age-sex classes show differing seasonal patterns."))
p
```

@@

p <- ggplot(plot_df,aes(day,solar_hour,fill=ho_prob))+
  geom_tile(color= "white",size = 0) +
  scale_fill_gradientn(colors = rev(met.brewer("Hiroshige")),
                       name = "haul-out probability", aesthetics = "fill",
                       limits = c(0,1), breaks = c(0.25, 0.50, 0.75),
                       guide = guide_colorbar(title.position = "bottom", barwidth = 15,
                                              barheight = 0.5, title.hjust = 0.5)
  # scale_fill_viridis_c(name = "haul-out probability", aesthetics = "fill",
  #                      guide = guide_colorbar(title.position = "bottom", barwidth = 15,
  #                                             barheight = 0.5, title.hjust = 0.5)
  )
p <- p + facet_grid(age_sex~month)
p <- p + scale_x_continuous(breaks = c(1,10,20,30)) +
  scale_y_continuous(breaks = c(4,12,20))
p <- p + theme(legend.position = "bottom") +
  theme(strip.background = element_rect(colour="white")) +
  theme(axis.ticks=element_blank()) +
  xlab("day of month") + ylab("local solar hour") +
  ggtitle("Spotted seal predicted haul-out probability.",
          subtitle = str_wrap("Periods of highest haul-out probability for spotted seals appear centered around solar noon and age-sex classes show differing seasonal patterns."))
p
```
